Exp1 - Opt w_max and {A,phi)

### 2018-04-06 voltagebudget/analysis/paper_figures.Rmd
Update Fig 3

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=.6) +
  scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
  # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
  geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(
    legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

@@

plot_grid <- rbind(
  c(NA),
  c(1, 2),
  c(1, 2),
  c(3, 3),
  c(3, 3),
  c(3, 3))

grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

```{r, fig.width=0.4, fig.height=1.2}
fig14 %>% 
  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
  geom_line(size=0.3, color="darkgrey") +
  facet_grid(cell~.) +
  theme_classic() +
  labs(x="Time (s)", y="V (mV)") +
  theme(
    strip.text = element_blank(),
    strip.background = element_blank(),
    legend.position="none",
    axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    plot.background=element_blank())
```

>>>>

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=(variances_pop/n_spikes_pop)*1e3, color=V_osc/V_b)) +
  geom_point(size=0.2, alpha=.6) +
  scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
  # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
  geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(
    legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

@@

plot_grid <- rbind(
  c(NA),
  c(3, 3))

grid.arrange(p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

```{r, fig.width=0.4, fig.height=1.2}
fig14 %>% 
  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
  geom_line(size=0.2, color="black") +
  facet_grid(cell~.) +
  theme_classic() +
  labs(x="Time (s)", y="V (mV)") +
  theme(
    strip.text = element_blank(),
    strip.background = element_blank(),
    legend.position="none",
    axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    plot.background=element_blank())
```
